---
title: "CDS 431 Spring 2022 Survey Data"
output: 
    html_document:
      theme: spacelab
      highlight: tango
      toc: TRUE
      toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r setup 1, include=FALSE}
library(tidyverse)
library(rio)
library(here)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(SCVA)
library(patchwork)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )

```

```{r, include=FALSE}
gtky <- import(here("data", "get_to_know.sav"),
               setclass = "tbl_df") %>% 
  characterize() %>% 
  janitor::clean_names()

str(gtky)

gtky[sapply(gtky, is.character)] <- lapply(gtky[sapply(gtky, is.character)],
                                                 as.factor)

str(gtky)
```


## Get to Know You

### What state are you from?

```{r, include=FALSE}

state <- gtky %>% 
  group_by(q1) %>% 
  count()

state$q1 <- factor(state$q1, levels = c("California",
                                        "Oregon",
                                        "Washington",
                                        "Other"))

state_plot <- state %>% 
  ggplot(aes(q1, n)) +
  geom_col(fill = "#56B4E9",
             alpha = 0.7) +
  geom_text(aes(q1, n, label = n),
            size = 4,
            nudge_y = -1.0,
            nudge_x = 0.3) +
  labs(x = "State",
       y = "Total")
```

```{r, include=TRUE}
state_plot
```

Other locations include: 

  * Alaska
  * Arizona
  * Hawaii
  * Ohio
  * Utah
  * Harbin, China
  
  
### Are you an undergraduate or post bac student?

```{r, include=FALSE}
str(gtky)

stu_type <- gtky %>% 
  group_by(q2) %>% 
  count()


stu_plot <- stu_type %>% 
  ggplot(aes(q2, n)) +
  geom_col(fill = "#56B4E9",
             alpha = 0.7) +
  scale_y_continuous(limits = c(0, 50),
                     breaks = c(0, 10, 20, 30, 40, 50)) +
  geom_text(aes(q2, n, label = n),
            size = 4,
            nudge_y = 2.0,
            nudge_x = 0.3) +
  labs(x = "",
       y = "Total")
```

```{r, include=TRUE}
stu_plot
```


### Which career do you want to pursue?

```{r, include=FALSE}
gtky$q3

career <- gtky %>% 
  group_by(q3) %>% 
  count()

career$q3 <- factor(career$q3, levels = c("Audiology",
                                        "Speech-Language Pathology",
                                        "Other"))

career_plot <- career %>% 
  ggplot(aes(q3, n)) +
  scale_y_continuous(limits = c(0, 50),
                     breaks = c(0, 10, 20, 30, 40, 50)) +
  geom_col(fill = "#56B4E9",
             alpha = 0.7) +
  geom_text(aes(q3, n, label = n),
            nudge_y = -1.0,
            nudge_x = 0.3, 
            size = 4) +
  labs(x = "",
       y = "Total")
```

```{r, include=TRUE}
career_plot
```

Other career plans include: 

  * Masters in fitness
  * Law enforcement 
  * Special education 
  * Occupational therapy 

### What is your preferred work setting?

```{r, include=FALSE}
gtky$q4

setting <- gtky %>% 
  group_by(q4) %>% 
  count()

setting_plot <- setting %>% 
  ggplot(aes(q4, n)) +
  scale_y_continuous(limits = c(0, 25),
                     breaks = c(0, 5, 10, 15, 20, 25)) +
  geom_col(fill = "#56B4E9",
             alpha = 0.7) +
  geom_text(aes(q4, n, label = n),
            nudge_y = -1.0,
            nudge_x = 0.3, 
            size = 4) +
  labs(x = "",
       y = "Total") + 
  theme(axis.text.x=element_text(angle=45,hjust=1))
```

```{r, include=TRUE}
ggplotly(setting_plot)
```

### What age group are you most interested in working with?

```{r, include=FALSE}
gtky$q5

age_group <- gtky %>% 
  group_by(q5) %>% 
  count()


age_group$q5 <- factor(age_group$q5, levels = c("Birth through age 5",
                                        "Kindergarten through Grade 12",
                                        "Adults 18-65",
                                        "Adults 65 and older"))

age_group_plot <- age_group %>% 
  ggplot(aes(q5, n)) +
  scale_y_continuous(limits = c(0, 25),
                     breaks = c(0, 5, 10, 15, 20, 25)) +
  geom_col(fill = "#56B4E9",
             alpha = 0.7) +
  geom_text(aes(q5, n, label = n),
            nudge_y = 2.0,
            nudge_x = 0.3, 
            size = 4) +
  labs(x = "",
       y = "Total") +
    theme(axis.text.x=element_text(angle=45,hjust=1))
```

```{r, include=TRUE}
ggplotly(age_group_plot)
```

### What type of communication disorder most interests you?

```{r, include=FALSE}
gtky$q6

fav_dis <- gtky %>% 
  group_by(q6) %>% 
  count() 


fav_dis_plot <- fav_dis %>% 
  ggplot(aes(fct_reorder(q6, n), n)) +
  scale_y_continuous(limits = c(0, 25),
                     breaks = c(0, 5, 10, 15, 20, 25)) +
  geom_col(fill = "#56B4E9",
             alpha = 0.7) +
  geom_text(aes(q6, n, label = n),
            nudge_y = 1.5, 
            size = 4) +
  coord_flip() +
  labs(x = "",
       y = "Total")
```

```{r, include=TRUE, fig.width=15}
ggplotly(fav_dis_plot)
```